\subsection{Milestones of the EIP Planning}

This milestones ensemble is shared by all the groups, because it's imposed by the EIP planning.


A first family of milestones is composed of the architecture reports AA1 and AA2, on 2013 June 20 and September 1st, respectively. These milestones will thus lead us to make a final choice among the possibilities for the project's architecture.

A second one concerns normal and final technical reports, regularly spreaded out from 2013 November to 2015 January. They will match specific milestones for our projects and shall mark important decisions, like a category finalization.

Finally, the third one holds together the two final defenses, the 4th year one in 2014 September, and the 5th year one in 2015 February. Both of them will represent a project shipping, of an advanced version for the first one, and of a final version for the second one.


\subsection{Specific milestones of the Onitu project}

These milestones are defined by our project and thus mark its important points. They are to be put in relationship with the previous groupment, since the latter represent important dates at which these points shall be completed.


First of all, it will be necessary to have a minimal testing client, to permit the server development, along with the client's one.

Next, the obtention of a working, then complete server will stand as two very important steps of the project.

The last two milestones concern clients, and match the finalization of the official client's fork and of the Web UI.


\subsection{Categories definition}

Our categorizing is made of the different parts of the project, which contain: the Ubuntu One official client's fork (adding the choice of the server to use), the web UI (complete managing interface, with file sharing), the server (conception and realization of the APIs and of the database), and drivers (giving access to both internal and external resources for data storage).